Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 mcmc.tex
started pass over mcmc

We model the probability that the object in the test image
$\mathcal{I}$ is generated by the parameters $x$ as a distribution in
the exponential family, and let
\begin{align}
    P(x) & \sim e^{ c_4 \max_{s} w(x) \ast \mathcal{T}_s(\mathcal{I})}.
\end{align}

We use Metropolis Hastings to optimize $x$.

We model the distribution of object location and pose as an exponential distribution.

@@

$P$ is the distribution of the pose and location of an object on image
$\mathcal{I}$. One can also think of the image as an image cropped by detection
bounding box. We synthesize covariance matrix and create NZ-WHO template $w(x)$ for particular viewpoint, focal length and CAD model.

@@

We represented the probability using exponential family.

So our model favors large convolution score $\max_{s} w(x) \ast T(\mathcal{I})$. 
% there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  
\begin{figure}[t]
\centering
    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
    \caption{Different modes of Metropolis Hasting proposals, see Section \ref{sec:fine}}
 \label{fig:tuningmode}
\end{figure}

>>>>

We model the probability that the object in the test image
$\mathcal{I}$ is generated by the parameters $x$ as a distribution in
the exponential family, and let
\begin{align}
    P(x) & \sim e^{ c_4 \max_{s} w(x) \ast \mathcal{T}_s(\mathcal{I})},
\end{align}
where $\max_{s} w(x) \ast T(\mathcal{I})$ is the convolution score of
template $w(x)$ with image feautures $T(\mathcal{I})$, as defined
in Sect.~\ref{}.

\paragraph{Inference.}
We approximate the MAP solution for $x$ by drawing samples from the
distribution $P(x)$, using the Metropolis-Hastings
algorithm. Specifically, we use a variant that changes only a single
component of the parameter vector $x$ at a time, termed Single
Component Metropolis Hastings.

As proposals

@@

$P$ is the distribution of the pose and location of an object on image
$\mathcal{I}$.

One can also think of the image as an image cropped by detection
bounding box. We synthesize covariance matrix and create NZ-WHO
template $w(x)$ for particular viewpoint, focal length and CAD model.

% there are several advantages that was not possible such as
% \textbf{on-the-fly} template generation and making large number of
% templates
\begin{figure}[t]
\centering
    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
    \caption{Different modes of Metropolis Hasting proposals, see Section \ref{sec:fine}}
 \label{fig:tuningmode}
\end{figure}

@@
